Reinforcement Learning Based Transmitter-Receiver Selection for Distributed MIMO Radars

### 2020-01-17 paper.tex
Updates from Overleaf

A Distributed multiple-input and multiple-output (MIMO) radar is a system in which multiple transmitters and receivers are deployed in different locations \cite{distributed}.
The widely distributed antennas increase spatial diversity which can be utilized for improved target localization, parameter estimation and detecting low-observable targets.
In a MIMO radar, the used waveforms are designed jointly and the waveforms are typically orthogonal.
Therefore, each transmitter-receiver (TX-RX) pair forms an independent channel for illuminating and observing the targets.
Increasing the number of channels provides additional spatial diversity at the cost of larger amount of data to be processed and higher power consumption \cite{antenna_subset_selection, selection_and_placement, aittomaki1}.
In addition, active transmitters may expose their location which might be undesired in certain applications.
Strategies for TX-RX subset selection are studied to preserve the spatial diversity and reduce the costs at the same time.

The TX-RX subset selection problem, especially for target localization, has been previously addressed in the literature \cite{antenna_subset_selection, selection_and_placement}.
In these studies, the signal-to-interference-plus-noise ratio (SINR) is assumed to be known or estimated.
It is possible to estimate the SINR based on assumed particular propagation environments and target models, but a real-world radar environment may deviate from the assumed model and consequently lead to performance degradation.

@@

This paper proposes a machine learning approach for the active TX-RX subset selection in the distributed MIMO radar context.
The problem is formulated as a multi-armed bandit (MAB) problem. 
The MAB framework provides policies for selecting actions to balance the exploration and exploitation trade-off while maximizing the employed reward function \cite{lattimorebandit}.
We use extensions from the combinatorial MAB framework to handle the exponentially growing action space and propose a generalized algorithm to solve the problem using any index-based MAB algorithm.

>>>>

A Distributed multiple-input and multiple-output (MIMO) radar is a system in which multiple transmitters and receivers are deployed in different locations \cite{Haimovich2008}.
The widely distributed antennas increase spatial diversity which can be utilized for improved target localization, parameter estimation and detecting low-observable targets.
In a MIMO radar, the used waveforms are designed jointly and the waveforms are typically orthogonal.
Therefore, each transmitter-receiver (TX-RX) pair forms an independent channel for illuminating and observing the targets.
Increasing the number of channels provides additional spatial diversity at the cost of larger amount of data to be processed and higher power consumption \cite{Godrich2011, Sun2014, Aittomaeki2018}.
In addition, active transmitters may expose their location which might be undesired in certain applications.
Strategies for TX-RX subset selection are studied to preserve the spatial diversity and reduce the costs at the same time.

The TX-RX subset selection problem, especially for target localization, has been previously addressed in the literature \cite{Godrich2011, Sun2014}.
In these studies, the signal-to-interference-plus-noise ratio (SINR) is assumed to be known or estimated.
It is possible to estimate the SINR based on assumed particular propagation environments and target models, but a real-world radar environment may deviate from the assumed model and consequently lead to performance degradation.

@@

This paper proposes a machine learning approach for the active TX-RX subset selection in the distributed MIMO radar context.
The problem is formulated as a multi-armed bandit (MAB) problem. 
The MAB framework provides policies for selecting actions to balance the exploration and exploitation trade-off while maximizing the employed reward function \cite{Lattimore2019}.
We use extensions from the combinatorial MAB framework to handle the exponentially growing action space and propose a generalized algorithm to solve the problem using any index-based MAB algorithm.
